Tree Graphs Test

### 2021-07-14 tests/testgraphs.Rmd
Added reorder of position for bar graph

```{r}
z <- tree_diameter1 %>%
  ggplot(aes(x=position, y=diameter, fill=species)) +
  geom_bar(stat="identity", position="dodge") +
  scale_y_continuous(limits = c(0, 60))
z
```

@@

```{r}
w2 <- tree_diameter1 %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Eastern Hemlock"))
w2
```

>>>>

```{r}
z <- tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                            "emergent", "canopy", "subcanopy", "sapling")) %>%
  ggplot(aes(x=position, y=diameter, fill=species)) +
  geom_bar(stat="identity", position="dodge") +
  scale_y_continuous(limits = c(0, 60))
z
```

@@

```{r}
w2 <- tree_diameter1 %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  coord_flip() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Eastern Hemlock"))
w2
```
